\documentclass [a4paper,11pt]{article}
%\usepackage{fontspec}
\pagestyle {empty}
\usepackage[a4paper,margin=1.10in]{geometry}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}

\newcommand{\landmark}[1]{{{#1}}}
\newcommand{\company}[1]{{\textbf{#1}}}

\begin {document}

	\begin {center}
		\begin {tabular} {c}
			\textbf {\Large {GIORGOS TZAMPANAKIS}} \\
			\\
				\begin {tabular} {rl}
					\textbf {Date of Birth:} & 20 August 1984 \\
					\textbf {Address:} & 2, Theotoki Str., Flat 301 \\
							& 1055, Nicosia, Cyprus \\
					\textbf {Telephone:} & +357~22~349~783 \\
					\textbf {Mobile:} & +357~96~683~803 \\
					\textbf {Email:} & Giorgos.Tzampanakis@gmail.com \\
					%\textbf {Date of Birth:} & 20th August 1984 \\
					%\textbf {Address:} & Room 230, Lord Thomson Hall \\
					%		& Heriot-Watt University \\
					%		& PO Box 28600, Riccarton \\
					%		& Edinburgh EH14~4YJ \\
					%\textbf {Landline:} & 0844~546~5950 \\
					%\textbf {Email:} & Giorgos.Tzampanakis@gmail.com \\
				\end {tabular} \\
		\end {tabular}
	\end {center}

	\medskip

	\section* {Education}
		\begin {description}
		\parindent=20pt

			\item [2009--2010,] \company{Heriot-Watt University, Edinburgh},
			MSc in Information Technology (Applied Systems) with Distinction
			(received A grade in all 8 modules).  The title of my MSc Project
			was ``From Gates to RISC: Digital Logic and Computer Architecture
			Experiments for an Enhanced Student Learning Experience''.

			%	\begin {table} [ht]
			%		\begin {center}
			%			\begin {tabular} {l|l}
			%				\textbf {Module} & \textbf {Mark} \\
			%				\hline
			%				Digital Signal Processing & 72\% \\
			%				Software Engineering I & 87\% \\
			%				Digital Design & 82\% \\
			%				Research Methods & 72\% \\
			%				Image Processing & 84\% \\
			%				Software Engineering II & 82\% \\
			%				Embedded Software & 71\% \\
			%				MSc Project & 78\% \\
			%				\hline
			%			\end {tabular}
			%		\end {center}
			%	\end {table}


			\item [2003--2009,] \company{Technological Educational Institute
			of Piraeus, Greece}, Degree in Electrical Engineering with final
			grade ``Very Well'', 6.74/10. The title of my dissertation was
			``Analysis of Nonlinear Circuits'' and it presented algorithms and
			data structures used when analysing such circuits on computer
			SPICE-like systems.

		 \end {description}
	
	\section* {Employment}
		\begin {description}

			\item [August 2015--now:] \landmark{Python Developer} at
			\company{Wargaming.net} in Ni\-co\-si\-a, Cyprus, implementing an
			internal Payment System project.

			\item [September 2014--August 2015:] \landmark{Billing Developer} at
			\company{Playtech} in Ni\-co\-si\-a, Cyprus.  Playtech is an online
			gaming company; it was in the process of overhauling its billing
			process, introducing more automation and interfacing with external
			billing software. My role was the main software development
			resource of the billing team.

			\item [September 2013--September 2014:] \landmark{Senior
			Programming Subject Matter Expert} at \company{Amdocs} in
			Li\-ma\-ssol, Cyprus.  I was assigned to the Revenue Management
			division, and more specifically to the Accounts Receivable (AR)
			module. AR leverages the Weblogic Java EE application server and
			the Oracle database to manage payments for very large
			telecommunication companies.

			\item [April 2013--July 2013:] \landmark{Software Developer} at
			\company{Qobo} in Ni\-co\-si\-a, Cyprus.  Qobo is a startup that
			aims to offer business software solutions.  The company being in
			their planning stage, my duties were primarily to evaluate Java
			frameworks that could be used by the company.

			\item [November 2010--January 2013:] \landmark{Software developer}
			at \company{CRM.COM} in Ni\-co\-si\-a, Cyprus. CRM.COM is Customer
			Relationship and Billing Management software for Pay TV, Retail,
			Energy and other industries. Technologies that I worked with daily
			included Java EE, SQL, Hibernate, Jasper Reports and many more. 
			% The CRM.COM software can work with three different databases, IBM
			% DB2, Oracle and MS SQL Server, thus I interacted with those three
			% databases on a daily basis.

			\item [June 2008--December 2008:] \landmark{Shift Engineer} at Hospital
			``Attikon'' in Athens, working for private contractor \company{MELKAT}
			(fulfilling the 6 months of employment that was a mandatory part of
			my Electrical Engineering degree).  My duties were mostly to monitor
			and operate the heating and cooling systems of the hospital via Honeywell's
			Building Management System.

		\end {description}

	\section* {Skills}
		\begin {description}
			\item [Programming languages:] Python, Java, Javascript, C, C++, bash, SQL.
			\item [Libraries:] JavaEE, jQuery, Hibernate, Django.
			\item [Database Management Systems:] SQLite, Oracle, MS SQL Server, IBM DB2, MySQL.
			\item [Web:] HTML, CSS.
			\item [Mathematical Software:] MATLAB, Numpy, Scipy, R, Mathematica, Octave, Maxima.
			\item [Operating Systems:] Windows, Linux.
			\item [HDL:] Verilog HDL.
			\item [Document Preparation:] \LaTeX , Office, OpenOffice.org.
		\end {description}

	% \section* {Languages}
	% 		\begin {description}
	% 			\item [Greek:] Native.
	% 			\item [English:] Fluent.
	% 		\end {description}

	\section* {Code Samples / Released Software}
		\begin {itemize}

			\item Code samples can be found at \url{https://github.com/gtzampanakis}.

			\item A Python implementation of the FastSS string similarity
			calculation algorithm. It is the first Python implementation of the
			algorithm. Available (along with source code) at
			\url{http://pypi.python.org/pypi/fastss}.

			\item HTTP downloader utilising a compressed disk cache. Ideal for
			use in writing web scrapers. Available (along with source code) at
			\url{http://pypi.python.org/pypi/downloader}.

		\end {itemize}

	\section* {Websites}
		\begin {description}
			\item [\url{www.bgtrain.com}:] A backgammon training application;
			users are given position problems and their answers are evaluated
			against the computer analysis, which is provided by the GNU
			Backgammon engine.  The system subsequently uses a user's answer
			history to pick problems close to the his/hers playing strength.
			Also features a comments system and a leaderboard. Developed from
			scratch using Python and MySQL.
			\item [\url{www.statsfair.com}:] Regularly and automatically
			updated statistical ratings for the games of tennis and snooker.
			Playing strength can be plotted against time. Estimates of the win
			probability for each user-selected pair of players are also
			provided. A section of the website provides a live odds feed from a
			large bookmaker. Developed from scratch using Python and SQLite.
		\end {description}


	% \section* {Research}
	% 	\begin {itemize}
	% 		\item My primary research interest is predictive statistical modelling,
	% 		particularly via the method of paired comparisons.
	% 	\end {itemize}


	\section* {Background}
		\begin {itemize}
			\item My nationality is Greek and I come from Athens.
			\item My native language is Greek; my English is fluent.
			\item As a Greek citizen I can travel and work freely within the EU.
			\item I greatly enjoy working in problems that combine Engineering,
			Mathematics and Programming, especially Digital Signal Processing,
			Control Systems and Artificial Intelligence.
		\end {itemize}

\end {document}
